Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-06-28 output/latex/manuscript.tex
crispr: update FACS Jazz Softare version
fix coauthor affiliation

\textsuperscript{1} Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{2} Department of Biomedical Informatics, University of Colorado School of Medicine, Aurora, CO 80045, USA.
\textsuperscript{3} Center for Spatial and Functional Genomics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA.
\textsuperscript{4} Department of Biomedical Data Science, Stanford University, Stanford, CA, USA.
\textsuperscript{5} Vanderbilt University Medical Center.
\textsuperscript{6} Cincinnati Children's Hospital Medical Center.
\textsuperscript{7} Department of Medicine, Division of Nephrology, Vagelos College of Physicians \& Surgeons, Columbia University, New York, New York, USA.
\textsuperscript{8} Mayo Clinic.
\textsuperscript{9} Northwestern University.
\textsuperscript{10} School of Computing, University of Utah, Salt Lake City, UT, USA.
\textsuperscript{11} Department of Systems Pharmacology and Translational Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{12} Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{13} Institute for Translational Medicine and Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{14} Division of Endocrinology and Diabetes, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA.
\textsuperscript{15} Division of Human Genetics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA; Department of Pediatrics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA, 19104, USA.
\textsuperscript{16} Center for Health AI, University of Colorado School of Medicine, Aurora, CO 80045, USA.

@@

For the CRISPR screening, we used FlowJo v10.7 and FACS Jazz software v1.0.
For data analysis, we used Python 3.8 and R 3.6 with several computational packages.
The main Python packages used were: Jupyter Lab (2.2), pandas (1.1), matplotlib (3.3), seaborn (0.11), numpy (1.19), scipy (1.5), scikit-learn (0.23), and umap-learn (0.4).
The main R packages were: Bioconductor (3.10), clusterProfiler (3.14), clustree (0.4), and fgsea (1.17).
We also developed several scripts and notebooks which are published under an open-source license.
We documented all the steps necessary to carry out all the analyses.
We also provide a Docker image to use the same runtime environment we used, and a demo to quickly test the methods on real data.

>>>>

\textsuperscript{1} Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{2} Department of Biomedical Informatics, University of Colorado School of Medicine, Aurora, CO 80045, USA.
\textsuperscript{3} Center for Spatial and Functional Genomics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA.
\textsuperscript{4} Department of Biomedical Data Science, Stanford University, Stanford, CA, USA.
\textsuperscript{5} Vanderbilt University Medical Center.
\textsuperscript{6} Cincinnati Children's Hospital Medical Center.
\textsuperscript{7} Department of Medicine, Division of Nephrology, Vagelos College of Physicians \& Surgeons, Columbia University, New York, New York, USA.
\textsuperscript{8} Mayo Clinic.
\textsuperscript{9} Northwestern University.
\textsuperscript{10} Kahlert School of Computing, University of Utah, Salt Lake City, UT, USA.
\textsuperscript{11} Department of Systems Pharmacology and Translational Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{12} Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{13} Institute for Translational Medicine and Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{14} Division of Endocrinology and Diabetes, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA.
\textsuperscript{15} Division of Human Genetics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA; Department of Pediatrics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA, 19104, USA.
\textsuperscript{16} Center for Health AI, University of Colorado School of Medicine, Aurora, CO 80045, USA.

@@

For the CRISPR screening, we used FlowJo v10.7 and FACS Jazz Software v1.1.
For data analysis, we used Python 3.8 and R 3.6 with several computational packages.
The main Python packages used were: Jupyter Lab (2.2), pandas (1.1), matplotlib (3.3), seaborn (0.11), numpy (1.19), scipy (1.5), scikit-learn (0.23), and umap-learn (0.4).
The main R packages were: Bioconductor (3.10), clusterProfiler (3.14), clustree (0.4), and fgsea (1.17).
We also developed several scripts and notebooks which are published under an open-source license.
We documented all the steps necessary to carry out all the analyses.
We also provide a Docker image to use the same runtime environment we used, and a demo to quickly test the methods on real data.
